### 2015-12-17 doc/manual/inputParameters.tex

>>>>

\param{preconditioner\_magnetic\_drifts\_max\_L}
{integer}
{2}
{Whenever \parlink{useIterativeLinearSolver} = \true and \parlink{magneticDriftScheme}$>0$}
{Maximum Legendre mode number for which the poloidal and toroidal magnetic drift terms are included in the preconditioner.
As this parameter is increased, more memory is required for factorization, but fewer KSP iterations are required.
Setting this parameter to $\ge$ \parlink{Nxi} means that the magnetic drifts are always included in the preconditioner.
Setting this parameter to $<0$ means the magnetic drifts are never included in the preconditioner.
The default value should be good.}
